### 2024-11-25 paper/main.tex
redid everything for submission to jnp

\vspace{10mm}
\noindent \boldblue{{{Decision-Making Models}}}

@@

Each model has varying knowledge of the different parameters (\boldblue{Fig. 3}, left column). A model can have full knowledge or partial knowledge of a particular parameter. With full knowledge, the decision policy fully utilizes the parameter when selecting the time to transition from reacting to guessing. With partial knowledge, the decision policy utilizes its partial and imperfect representation of the parameter. Here the idea is that a human may have an imperfect representation of some parameter when determining a transition time, even though that particular parameter will still influence behaviour. As an example, one could plan for only some portion of a time delay, but then end up deciding too late because they did not fully account for the entire time delay. All model parameter values and the fitting procedure are described in \boldblue{Supplementary C}.

@@

% \vspace*{2mm}
\noindent\emph{{No Switch Time Model}}

@@

\vspace*{2mm}
\noindent\emph{{{Full Switch Time Model}}}

@@

\vspace*{2mm}
\noindent\emph{{{Partial Switch Time Model}}}

@@

\noindent For all conditions, participants controlled a visible cursor that was aligned with their hand position. They started each trial by moving their cursor into a start position. Trial onset began with the appearance of both the stimulus (yellow cursor) and two targets. Participants could experience two trial types: react trials or guess trials. In the react trials, participants saw the stimulus move and were instructed to as quickly as possible follow the stimulus to one of the targets (\boldblue{Fig. 4A}). In the guess trials, participants saw the stimulus disappear from the start circle. They were instructed to guess one of the two targets as quickly as possible (\boldblue{Fig. 4B}). Following trial onset, the movement or disappearance of the stimulus was drawn from a normal distribution with a mean of 800ms and a standard deviation of 50ms. There were three experimental conditions (\boldblue{Fig. 4C}): the \emph{react or guess} condition, the \emph{only react} condition, and the \emph{only guess} condition.

\begin{figure}[H]
  \centering
  \includegraphics[scale = 1]{figures/exp2_design.png}

  \caption*{\boldblue{Figure 4: Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1. \boldblue{A)} Participants responded to two different types of stimuli. In the react trials (pink), the stimulus (yellow cursor) would move to one of the two potential targets. Participants were instructed to reach the same target as the stimulus as quickly as possible. \boldblue{B)} In the guess trials (blue), the stimulus disappeared from the start position. Once the stimulus disappeared, participants were instructed to guess which target the stimulus would appear in and select that target as quickly as possible. After the participant reached the target, the stimulus cursor would appear in one of the targets. \boldblue{C)} We had three experimental conditions. In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials). Participants were informed that the stimulus would either move to one of the targets or disappear. In the \emph{only react} condition, participants were informed that the stimulus would alway move to one of the two targets (50 react trials and 0 guess trials). They were also told that the stimulus would not disappear. In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials). They were also informed the stimulus would not move. }
\end{figure}

\noindent In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials). Participants were informed that the stimulus would either move to one of the targets or disappear. In the \emph{only react} condition, participants were informed that the stimulus would always move to one of the two targets (50 react trials and 0 guess trials). They were also told that the stimulus would not disappear. In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials). They were also informed that it would not move to one of the two targets.

During the \emph{react or guess} condition, we reasoned that participants would prefer to react because they would be guaranteed to select the correct target. As a result, in the \emph{react or guess} condition, if the stimulus disappeared the participant would switch from reacting to guessing when selecting a target. Conversely, during the \emph{only guess} condition, if the stimulus disappeared participants would not have to switch from reacting to guessing. Thus, if there is a delay when switching from reacting to guessing, we would expect a greater response time for the guess trials in the \emph{react or guess} condition compared to the guess trials in the guess only condition.

\noindent \boldblue{Response Time}

>>>>

\vspace{1mm}
\noindent \boldblue{{{Decision-Making Models}}}

@@

Each model has varying knowledge of the different parameters (\boldblue{Fig. 3}, left column). A model can have full knowledge or partial knowledge of a particular parameter. With full knowledge, the decision policy fully utilizes the parameter when selecting the time to transition from reacting to guessing. With partial knowledge, the decision policy utilizes its partial and imperfect representation of the parameter.

@@

\noindent Here the idea is that a human may have an imperfect representation of some parameter when determining a transition time, even though that particular parameter will still influence behaviour. As an example, one could plan for only some portion of a time delay, but then end up deciding too late because they did not fully account for the entire time delay. All model parameter values and the fitting procedure are described in \boldblue{Supplementary C}.

\vspace*{1mm}
\noindent\emph{{No Switch Time Model}}

@@

\vspace*{1mm}
\noindent\emph{{{Full Switch Time Model}}}

@@

\vspace*{1mm}
\noindent\emph{{{Partial Switch Time Model}}}

@@

\noindent For all conditions, participants controlled a visible cursor that was aligned with their hand position. They started each trial by moving their cursor into a start position. Trial onset began with the appearance of both the stimulus (yellow cursor) and two targets. Participants could experience two trial types: react trials or guess trials. In the react trials, participants saw the stimulus move and were instructed to as quickly as possible follow the stimulus to one of the targets (\boldblue{Fig. 4A}). In the guess trials, participants saw the stimulus disappear from the start circle. They were instructed to guess one of the two targets as quickly as possible (\boldblue{Fig. 4B}). Following trial onset, the movement or disappearance of the stimulus was drawn from a normal distribution with a mean of 800ms and a standard deviation of 50ms. There were three experimental conditions (\boldblue{Fig. 4C}): the \emph{react or guess} condition, the \emph{only react} condition, and the \emph{only guess} condition. In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials). Participants were informed that the stimulus would either move to one of the targets or disappear. In the \emph{only react} condition, participants were informed that the stimulus would always move to one of the two targets (50 react trials and 0 guess trials). They were also told that the stimulus would not disappear. In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials). They were also informed that it would not move to one of the two targets.

During the \emph{react or guess} condition, we reasoned that participants would prefer to react because they would be guaranteed to select the correct target. As a result, in the \emph{react or guess} condition, if the stimulus disappeared the participant would switch from reacting to guessing when selecting a target. Conversely, during the \emph{only guess} condition, if the stimulus disappeared participants would not have to switch from reacting to guessing. Thus, if there is a delay when switching from reacting to guessing, we would expect a greater response time for the guess trials in the \emph{react or guess} condition compared to the guess trials in the guess only condition.
\begin{figure}[H]
  \centering
  \includegraphics[scale = 1]{figures/exp2_design.png}

  \caption*{\boldblue{Figure 4: Experiment 2 Design.} The goal of this experiment was to test the idea that there is a delay and uncertainty associated with switching from reacting to guessing, as suggested by our findings in  Experiment 1. \boldblue{A)} Participants responded to two different types of stimuli. In the react trials (pink), the stimulus (yellow cursor) would move to one of the two potential targets. Participants were instructed to reach the same target as the stimulus as quickly as possible. \boldblue{B)} In the guess trials (blue), the stimulus disappeared from the start position. Once the stimulus disappeared, participants were instructed to guess which target the stimulus would appear in and select that target as quickly as possible. After the participant reached the target, the stimulus cursor would appear in one of the targets. \boldblue{C)} We had three experimental conditions. In the \emph{react or guess} condition, react trials and guess trials were randomly interleaved (50 react trials and 50 guess trials). Participants were informed that the stimulus would either move to one of the targets or disappear. In the \emph{only react} condition, participants were informed that the stimulus would alway move to one of the two targets (50 react trials and 0 guess trials). They were also told that the stimulus would not disappear. In the \emph{only guess} condition, participants were informed that the stimulus would always disappear (0 react trials and 50 guess trials). They were also informed the stimulus would not move. }
\end{figure}
\noindent \boldblue{Response Time}
